---
title: "My first analysis: A report"
author: Ron Lewis #quotes used when ambiguity with syntax such as commas or colons 
date: "Friday, March 25, 2022"
output: 
  pdf_document:
    keep_tex: true #generates tex file for review
    toc: true 
header-includes:
  - \usepackage{booktabs}
bibliography: refs.bib
biblio-style: apalike
---

```{r, echo = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE , echo = FALSE)

```

```{r libraries}
library(tidyverse)
library(knitr)
library(kableExtra)

```

Just mods to track with commits 11:54

data_df <- tibble(y = rnorm(100),
                  x = runif(100))

ggplot(data_df, aex(x = x, y = y)) + geom_point()

ggplot(data_df, aex(x = x)) + geom_point

# Introduction

This is my *introduction*.

## Hypothesis

This is my **hypothesis**. I've added to it just to have some change in this file for git'ing puposes.

### Main hypothesis

This ***main hypothesis*** is always \underline{hardest} to establish.

```{r my_figure, fig.cap = 'Caption is "here". For this smashing scatterplot.' , out.width = "0.5\\textwidth", fig.align = "center"}
data_df <- tibble(x = rnorm(10),
                  y = rnorm(10))

ggplot(data_df, 
       aes(x = x, y = y)) + geom_point() + theme_classic() 
```
 
```{r}
 
# data_summary <- data_df %>%
#    summarise_all(list(mean = mean, sd = sd)) 
#   rename_all(~str_replace_all(., '_', ''))

 data_summary <- select(diamonds, color, clarity, depth, price) %>% slice(1:10)

# kable(data_summary,
#       format = 'latex',
#       digits = 2,
#       booktabs = TRUE) %>%
#   kable_styling(position = "center")

make_table <- function(data){
  kable(data,
      format = 'latex',
      digits = 2,
      booktabs = TRUE) %>%
  kable_styling(latex_options = "HOLD_position", position = 'center')
}

make_table(data_summary)
```

```{r, comment = ''}
M <- lm(y ~ x, data = data_df)
S <- summary(M)

make_table(S$coefficients)
# 
# kable(S$coeffecients,
#       format = "latex",
#       digits = 2,
#       booktabs = TRUE) 

# %>%
  # kable_styling(position = "center")
```

From this analysis, $$R^2 = `r round(S$r.squared, 2)`$$

Hereis a [link](http://www.vocm.com).

As was shown in @andrews2014reconciling where that fellow did this. Whereas @schneider2009quantitative shows this other thing.

```python
X = []
for x in range(x):
  X.append(x)

```

```{r, eval=FALSE, echo=TRUE}
M <- brm(y ~ x, data = data_df)
```

# A list of things

* Blue
* Red
* Green
* Rose

## More colours

* Blue
  * Light blue
  * Navy blue
  * Baby blue
* Green
  * Forest green
  * Emerald
  * Kelly green
  * Light green

# Numbered list

1. Blue
1. Red
1. Green
1. Rose
1. Orange
1. Purple

## Number list two

1. Blue
    1. Red
    1. Mauve
    1. Peackock
3. Green
    1. Rose
    1. Orange
    17. Purple

# The statistical model

Our model is
$$
y_i \sim \alpha + \beta x_i + \epsilon_i \longrightarrow \Phi_{\alpha_i}
$$

We use \LaTeX

# A definition list

height
: The person's height in cm

weight
: The person's weight in kg

age
: The person's age in years


# Bibliography
